---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


[![Travis-CI Build Status](https://travis-ci.org/mdsumner/scdb.svg?branch=master)](https://travis-ci.org/mdsumner/scdb)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/scdb?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/scdb)

# scdb

The goal of scdb is to provide a back-end for the sc project. 

This is a general common-form data structure for complex hierarchical data. 

## Installation

You can install scdb from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdsumner/scdb")
```

## Example

This is a basic example which converts a simple features object to a database, then recreates that object
in a very scaleable, flexible and extensible way. 

```{r example}

library(scdb)
library(scsf)
data(hpoly)
(pdb <- write_db(hpoly))
```

Now explore the objects available in the database. 

```{r}
library(dplyr)
(obj <- tbl(pdb, "object"))

```

There are three objects, and each has a long ID `object_`, as well as other metadata. 

Using joins we can access the other data in the decomposed tables. 

```{r joins}
(p <- tbl(pdb, "vertex") %>% inner_join(tbl(pdb, "path_link_vertex")) %>% inner_join(tbl(pdb, "path"))) 
```

In a real case we would wrap the chained joins within a  list-column in `obj` or similar trick, and use the database more cleverly to only 
expand out the data we need for each object. But also note there's  no `collect` statement, `big_tab` is still a promise that the database will do the work only when we really need it to. 

```{r recompose}
library(ggplot2)
collect(p) %>% ggplot(aes(x = x_, y = y_, group = path_, colour = path_)) + 
  geom_path()
```
